Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-09-02 paper/main.tex
more writing

\usepackage{amsmath,amssymb}
%\usepackage[square,numbers,sort&compress]{natbib}
\usepackage{xspace}
%% Useful packages
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage{multirow}
\usepackage{booktabs} % For formal tables
\usepackage{enumitem}
\usepackage{afterpage}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage[square,numbers,sort]{natbib}
% Fixes for using natbib and llncs
\makeatletter
% required for natbib to have "References" printed and as section*, not chapter*
\renewcommand\bibsection%
{\section*{\refname\@mkboth{\MakeUppercase{\refname}}{\MakeUppercase{\refname}}}}
\renewcommand\@biblabel[1]{#1.}
\makeatother

@@

We use the implementation of GECO provided by the
authors\footnote{\url{https://cran.r-project.org/package=CEGO}}. Following the
original paper~\citep{ZaeStoFriFisNauBar2014}, we use and the GA that optimizes
the surrogate models uses a population size of 20, crossover rate of 0.5,
mutation rate of 1, tournament selection of size 2 and probability of 0.9,
interchange mutation (i.e., exchanging two randomly selected elements of the
permutation) and cycle crossover for permutations. The budget of each run of
the GA is \textcolor{red}{10^5} evaluations using the surrogate-model. Although
it is never stated in the original paper, the implementation of CEGO generates
a set of initial solutions of size \minit by means of a
max-min-distance sequential design: new solutions are added to the set
sequentially by maximizing the minimum distance to solutions already in the
set. These initial solutions are then evaluated on the actual objective
function and the result is used to build the initial surrogate model.

@@

@@

\section*{Acknowledgements}

>>>>

\usepackage{amsmath,amssymb}
%\usepackage[square,numbers,sort&compress]{natbib}
\usepackage{xspace}
%% Useful packages
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage{multirow}
\usepackage{booktabs} % For formal tables
\usepackage{enumitem}
\usepackage{afterpage}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage[square,numbers,sort]{natbib}
% Fixes for using natbib and llncs
\makeatletter
% required for natbib to have "References" printed and as section*, not chapter*
\renewcommand\bibsection%
{\section*{\refname\@mkboth{\MakeUppercase{\refname}}{\MakeUppercase{\refname}}}}
\renewcommand\@biblabel[1]{#1.}
\def\bibfont{\small}
\makeatother

@@

We use the implementation of GECO provided by the
authors\footnote{\url{https://cran.r-project.org/package=CEGO}}. Following the
original paper~\citep{ZaeStoFriFisNauBar2014}, we use and the GA that optimizes
the surrogate models uses a population size of 20, crossover rate of 0.5,
mutation rate of 1, tournament selection of size 2 and probability of 0.9,
interchange mutation (i.e., exchanging two randomly selected elements of the
permutation) and cycle crossover for permutations. The budget of each run of
the GA is \textcolor{red}{$10^5$} evaluations using the surrogate-model. Although
it is never stated in the original paper, the implementation of CEGO generates
a set of initial solutions of size \minit by means of a
max-min-distance sequential design: new solutions are added to the set
sequentially by maximizing the minimum distance to solutions already in the
set. These initial solutions are then evaluated on the actual objective
function and the result is used to build the initial surrogate model.

@@

Bayesian optimization methods using a global GP model, such as CEGO, are know
to have trouble optimizing locally \citep{EriPeaGar2019scalable}. Our
intuition is that this problem becomes worse in rugged combinatorial
landscapes, where small steps may produce drastic changes.

@@

\paragraph*{Acknowledgements.}

Thanks to Hao Wang (Leiden University) for pointing us to the arguments of
\citet{EriPeaGar2019scalable}.
